---
title: "Analysis Title"
author: "Your Name"
date: "`r Sys.Date()`"
categories: [Analysis, GWAS, PRS]  # Modify based on the type of analysis
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
---

## **Overview**
_Provide a brief description of the analysis, its objectives, and key findings._

---

## **Methods**
### **Data Sources**
- Dataset: `dataset_name`
- Location: `/path/to/data/`
- Number of Samples: `XXX`

### **Analysis Steps**
1. Load the dataset
2. Perform QC and filtering
3. Generate visualizations
4. Summarize key findings

---

## **Results**
### **1️⃣ Interactive Table of Summary Statistics**
```{r}
library(DT)

# Dummy data
df <- data.frame(
  Sample = paste0("Sample_", 1:10),
  SNPs = sample(500000:1000000, 10),
  MissingRate = runif(10, 0, 0.05),
  Heterozygosity = runif(10, 0.3, 0.5)
)

datatable(df, options = list(pageLength = 5, scrollX = TRUE))

```


### **1️⃣ Interactive PCA Plot**
```{r}
library(plotly)

# Dummy PCA data
set.seed(123)
pca_data <- data.frame(
  Sample = paste0("Sample_", 1:50),
  PC1 = rnorm(50),
  PC2 = rnorm(50),
  Population = sample(c("Group A", "Group B"), 50, replace = TRUE)
)

p <- plot_ly(pca_data, x = ~PC1, y = ~PC2, color = ~Population, type = 'scatter', mode = 'markers', text = ~Sample)
p
```

### **Interpretation**
Summarize key findings, trends, and next steps.

### **Download & Reproducibility**
Full script: Download
Raw data: /path/to/results/
Re-run instructions:

---

### **🔹 How to Use This Template**
- Save it as `analysis_template.qmd` in your `analysis/` folder.  
- Copy and rename it for each new analysis (e.g., `gwas_qc.qmd`, `prs.qmd`).  
- Modify the **title, categories, and content**.  
- Update the **data and plots dynamically** based on new analyses.  

---

### **Next Steps**
1. **Would you like me to generate a Quarto project structure with sample analysis pages?**
2. **Do you need specific automation to pull data from your HPC?**

Let me know how to refine this further! 🚀
